%
% Embedded
% Embedded GNU/Linux Hardware
%
% LulzBot Easy TAZ Mini Developer's Guide
%
% Copyright (C) 2014 Aleph Objects, Inc.
%
% This document is licensed under the Creative Commons Attribution 4.0
% International Public License (CC BY-SA 4.0) by Aleph Objects, Inc.
%

\section{Overview}
The final hardware will be a custom built board by Linksprite (makers of the
PCDuino). The system will require two PCBs. One will be the (soon-to-be)
standard Linksprite Core Board. The other board is a daughter board to the
core board, and is a custom designed Base Board, populated with what we need
for the printer. This combo system we are calling the EZGNU.

\section{Specifications}
Specs, Core Board:

\begin{itemize}
  \item{Allwinner A20 ARM Processor}
  \item{1GHz CPU}
  \item{1 Gig RAM}
\end{itemize}

Specs, Base Board:
\begin{itemize}
  \item{MicroSD Card Slot}
  \item{4 USB A Ports}
  \item{Line level audio in/out}
  \item{Amplified audio out (mono speaker headers)}
  \item{Ethernet}
  \item{MIPI/CSI Camera socket}
  \item{10 GPIO pins}
  \item{24V power input}
  \item{12V RGB LED Strip driver}
  \item{uBoot button}
  \item{RST button}
  \item{DBG UART Pins}
  \item{LVDS LCD Socket}
  \item{I2C Touch screen socket}
\end{itemize}


\section{Other Hardware}

\subsection{LCD}
The LCD screen will mount near the EZGNU. The board is being specified by
Linksprite.

Specs LCD:

\begin{itemize}
  \item{HD resolution (1920x1080)}
  \item{LVDS interface}
\end{itemize}


\subsection{LED Lights}
There will be RBG LED strips to indicate various printer states via colored
lights.

\subsection{Camera}
The first version won't have a camera, though the EZGNU does have a header for
common types.

